Scheeper's Meager-NWD Game and the Menger Game

### 2014-08-25 phd/dissertation/_raw_chapter4.tex
Outline chapter 4,6
Name and camelCase based game commands/definitions

\begin{defn}
  For a uniform space $X$, the simplified proximal game $\proxgame{X}$ can be defined as follows:

@@

\begin{thm}
  $\pl D$ has a winning perfect-information strategy in Bell's game if and only if $\pl D\win\proxgame{X}$.
\end{thm}

@@

\begin{prop}
$\pl P$ has a winning perfect-information strategy in Bell's game if and only if $\pl P \win \proxgame{X}$.
\end{prop}

@@

\begin{defn}
  A uniform space is \textbf{proximal} if $\pl D \win \proxgame{X}$.
\end{defn}

\begin{defn}
  For a space $X$ and a point $x\in X$, the \textbf{$W$-convergence-game} $\congame{X}{x}$ proceeds as follows.

@@

\begin{defn}
  A space is \textbf{$W$} if $\pl O \win \congame{X}{x}$ for all $x\in X$.
\end{defn}

@@

\begin{thm}
For all $x\in X$:
  \begin{itemize}
    \item
      $\pl D\win \proxgame{X} \Rightarrow \pl O \win \congame{X}{x}$
    \item
      $\pl D\ktactwin{2k} \proxgame{X} \Rightarrow \pl O \ktactwin{k} \congame{X}{x}$
    \item
      $\pl D\kmarkwin{2k} \proxgame{X} \Rightarrow \pl O \kmarkwin{k} \congame{X}{x}$
  \end{itemize}
\end{thm}

\begin{proof}
Let $\sigma$ witness $\pl D \ktactwin{2k}\proxgame{X}$ (resp. $\pl D \kmarkwin{2k}\proxgame{X}$, $\pl D\win\proxgame{X}$). We define the $k$-tactical (resp. $k$-Mark\"ov, perfect info) strategy $\tau$ such that
  \[
    \tau\circ L_k(p)
      =
    \sigma\circ L_{2k}(\<x,p(0),\dots,x,p(|p|-1)\>)[x]
      \cap
    \sigma\circ L_{2k}(\<x,p(0),\dots,x,p(|p|-1),x\>)[x]
  \]
where $L_{2k}$ is the $2k$-tactical fog-of-war (resp. $2k$-Mark\"ov fog-of-war, identity) and $L_{k}$ is the $k$-tactical fog-of-war (resp. $k$-Mark\"ov fog-of-war, identity).

@@

Certainly, $x\in E_{2n}[x]= E_{2n}[q(2n)]$ for any $n<\omega$. Note also for any $n<\omega$ that 
    \[
      p(n) \in 
      \bigcap_{m\leq n}\tau\circ L_k(p\rest n)
    \]
    \[
      =
      \bigcap_{m\leq n}\left(
        \sigma\circ L_{2k}(\<x,p(0),\dots,x,p(m-1)\>)[x]\cap
        \sigma\circ L_{2k}(\<x,p(0),\dots,x,p(m-1),x\>)[x]
      \right)
    \]
    \[
      =
      \bigcap_{m\leq n}\left(
        D_{2m}[x]\cap
        D_{2m+1}[x]
      \right) =
      \bigcap_{m\leq 2n+1} D_m[x]=E_{2n+1}[x]
    \]
so by the symmetry of $E_{2n+1}$, $x\in E_{2n+1}[p(n)]= E_{2n+1}[q(2n+1)]$. Thus $x\in \bigcap_{n<\omega} E_n[q(n)]\not=\emptyset$, and since $\sigma$ is a winning strategy, the attack $q$ converges. Since $q(2n)=x$, $q$ must converge to $x$. Thus its subsequence $p$ converges to $x$, and $\tau$ is a winning strategy in $\congame{X}{x}$.
\end{proof}

\begin{cor}
For all $x\in X$:
  \begin{itemize}
    \item
      $\pl D\ktactwin{k} \proxgame{X} \Rightarrow \pl O \ktactwin{k} \congame{X}{x}$
    \item
      $\pl D\kmarkwin{k} \proxgame{X} \Rightarrow \pl O \kmarkwin{k} \congame{X}{x}$
  \end{itemize}
\end{cor}

@@

\begin{thm}
  Let $X\cup\{\infty\}$ be a uniformizable space such that $X$ is discrete. Then
  \begin{itemize}
    \item
      $\pl O\win \congame{X\cup\{\infty\}}{\infty} \Rightarrow \pl D \win \proxgame{X\cup\{\infty\}}$
    \item
      $\pl O\ktactwin{k} \congame{X\cup\{\infty\}}{\infty} \Rightarrow \pl D \ktactwin{k} \proxgame{X\cup\{\infty\}}$
    \item
      $\pl O\kmarkwin{k} \congame{X\cup\{\infty\}}{\infty} \Rightarrow \pl D \kmarkwin{k} \proxgame{X\cup\{\infty\}}$
  \end{itemize}
\end{thm}

@@

  Let $\sigma$ witness $\pl D \ktactwin{k}\congame{X\cap\{\infty\}}{\infty}$ (resp. $\pl D \kmarkwin{k}\congame{X\cap\{\infty\}}{\infty}$, $\pl D\win\congame{X\cap\{\infty\}}{\infty}$). We define the $k$-tactical (resp. $k$-Mark\"ov, perfect info) strategy $\tau$ such that
    \[
      \tau\circ L(p)
        =
      D(\sigma\circ L(p))
    \]
  where $L$ is the $k$-tactical fog-of-war (resp. $k$-Mark\"ov fog-of-war, identity).

@@

\begin{cor}
  Let $X\cup\{\infty\}$ be a uniformizable space such that $X$ is discrete. Then
  \begin{itemize}
    \item
      $\pl O\win \congame{X\cup\{\infty\}}{\infty} \Leftrightarrow \pl D \win \proxgame{X\cup\{\infty\}}$
    \item
      $\pl O\ktactwin{k} \congame{X\cup\{\infty\}}{\infty} \Leftrightarrow \pl D \ktactwin{k} \proxgame{X\cup\{\infty\}}$
    \item
      $\pl O\kmarkwin{k} \congame{X\cup\{\infty\}}{\infty} \Leftrightarrow \pl D \kmarkwin{k} \proxgame{X\cup\{\infty\}}$
  \end{itemize}
\end{cor}

\begin{prop} For any $x\in X$ and $k\geq 1$,
  \begin{itemize}
    \item
      $\pl O\ktactwin{k}\congame{X}{x} \Leftrightarrow \pl O\tactwin\congame{X}{x}$
    \item
      $\pl O\kmarkwin{k}\congame{X}{x} \Leftrightarrow \pl O\markwin\congame{X}{x}$
  \end{itemize}
\end{prop}

\begin{proof}
  If $\sigma$ witnesses $\pl O\ktactwin{k}\congame{X}{x}$, let $\tau(\emptyset)=\sigma(\emptyset)$ and
    \[
      \tau(\<q\>)
        =
      \bigcap_{i< k}
      \sigma(\<\underbrace{x,\dots,x}_{k-i-1},q,\underbrace{x,\dots,x}_{i}\>)
    \]

  This is easily verified to be a winning strategy. The proof for $\pl O\kmarkwin{k}\congame{X}{x}$ is analogous.
\end{proof}

\begin{cor}
  Let $X\cup\{\infty\}$ be a uniformizable space such that $X$ is discrete, and $k\geq 1$. Then
  \begin{itemize}
    \item
      $\pl D\ktactwin{k}\proxgame{X\cup\{\infty\}} \Leftrightarrow O\tactwin\proxgame{X\cup\{\infty\}}$
    \item
      $\pl D\kmarkwin{k}\proxgame{X\cup\{\infty\}} \Leftrightarrow O\markwin\proxgame{X\cup\{\infty\}}$
  \end{itemize}
\end{cor}

\begin{prop} For any uniform space $X$,
  \begin{itemize}
    \item
      $\pl O\ktactwin{k}\proxgame{X} \Leftrightarrow \pl O\ktactwin{2}\proxgame{X}$
    \item
      $\pl O\kmarkwin{k}\proxgame{X} \Leftrightarrow \pl O\kmarkwin{2}\proxgame{X}$
  \end{itemize}
\end{prop}

\begin{proof}
  If $\sigma$ witnesses $\pl O\ktactwin{k}\congame{X}{x}$, let $\tau(\emptyset)=\sigma(\emptyset)$ and
    \[
      \tau(\<q\>)
        =
      \bigcap_{i<k}
      \sigma(\<\underbrace{q,\dots,q}_{i}\>)
    \]
    \[
      \tau(\<q,q'\>)
        =
      \bigcap_{i< k}
      \sigma(\<\underbrace{q,\dots,q}_{k-i},\underbrace{q',\dots,q'}_{i}\>)
    \]

  This is easily verified to be a winning strategy. The proof for $\pl O\kmarkwin{k}\congame{X}{x}$ is analogous.
\end{proof}

@@

\begin{defn}
  The absolute proximal game $\aproxgame{X}$ is analogous to $\proxgame{X}$, except $\pl D$ may only win if $p$ converges.
\end{defn}

@@

\begin{thm}
  For any uniformly locally compact space $X$,
      $\pl D\win \proxgame{X} \Leftrightarrow \pl D\win \aproxgame{X}$
\end{thm}

\begin{proof}
  Let $M$ be a uniformly locally compact entourage. Let $\sigma$ witness $\pl D\win \proxgame{X}$ such that $\sigma(a)\subseteq M$ always (so $\cl{\sigma(a)[x]}\subseteq\cl{M[x]}$ is compact), and $a\supseteq b$  implies $\sigma(a)\subseteq\frac{1}{4}\sigma(b)$.

  Let $\tau(p\rest n)=\frac{1}{2}\sigma(p\rest n)$. If $p$ attacks $\tau$ in $\aproxgame{X}$, then
    \[
      p(n+1)
        \in
      \tau(p\rest n)[p(n)]
        =
      \frac{1}{2}\sigma(p\rest n)[p(n)]
    \]

@@

  Finally, note that $p$ attacks the winning strategy $\sigma$ in $\proxgame{X}$, but since the intersection of a chain of nonempty compact sets is nonempty:

@@

\begin{cor}
  A uniformaly locally compact space $X$ is proximal if and only if $\pl D \win \aproxgame{X}$.
\end{cor}

\begin{thm}
  For any uniformly locally compact proximal space $X$, $\pl O\win \clusgame{X}{H}$ for all compact $H\subseteq X$.
\end{thm}

\begin{proof}
  Let $\sigma$ witness $\pl D \win \aproxgame{X}$ such that $p\supseteq q$ implies $\sigma(p)\subseteq \frac{1}{4}\sigma(q)$.

@@

  With this we may define the perfect information strategy $\tau$ for $\pl O$ in $\congame{X}{H}$ such that:
  \[
    \tau(p\rest n) = \bigcup_{s\concat\<i,h_{s,i},j\>\in\max(T(p\rest n))} \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
  \]

@@

  Let $q'=\<i_0,h_0,j_0,x_0,i_1,h_1,j_1,x_1,\dots\>$ correspond to this infinite branch in $T(p)$, and let $q=o(q')=\<h_0,x_0,h_1,x_1,\dots\>$. Note that by the construction of $T(p)$, $q$ is an attack on the winning strategy $\sigma$ in $\aproxgame{X}$, so it must converge. Since every other term of $q$ is in $H$, it must converge to $H$. Then since $q$ is a subsequence of $p$, $p$ must cluster at $H$.
\end{proof}

\begin{cor}
  For any uniformly locally compact proximal space, $\pl O\win \congame{X}{H}$ for all compact $H\subseteq X$.
\end{cor}

\begin{proof}
  $\pl O \win \congame{X}{H}$ if and only if $\pl O \win \clusgame{X}{H}$.
\end{proof}

@@

\begin{thm}
  $\pl O \prewin \congame{X}{H}$ if and only if there exists a countable base 
  around $H$.
\end{thm}

@@

\begin{cor}
  $X$ is first countable if and only if $\pl O \prewin \congame{X}{x}$ for 
  all $x\in X$
\end{cor}

\begin{cor}
  $\pl D \prewin \proxgame{X}$ implies $X$ is first countable.
\end{cor}

@@

\begin{cor}
  If $X$ is scattered compact and $\pl O \prewin\congame{X}{x}$ for all
  $x\in X$ (or $\pl D \prewin\proxgame{X}$), then $X$ is metrizable.
\end{cor}

\begin{ex}
  $\pl D \not\prewin \proxgame{\oneptcomp\omega_1}$
\end{ex}

\begin{proof}
  There does not exist a countable base around $\infty$, so 
    $\pl O \not\prewin \congame{X}{\omega_1}$.
\end{proof}

\begin{ex}
  $\pl O \tactwin \congame{\oneptcomp\kappa}{\infty}$ and 
  $\pl D \tactwin \proxgame{\oneptcomp\kappa}$ for all cardinals $\kappa$
\end{ex}

\begin{proof}
  For $\congame{\oneptcomp\kappa}{\infty}$, let 
    $\sigma()=\sigma(\infty)=\oneptcomp\kappa$ 
  and 
    $\sigma(x)=\oneptcomp\kappa\setminus\{x\}$ 
  otherwise.
\end{proof}

@@

\begin{thm}
  If $H$ is a closed subset of $X$, then 
    $
      \pl D \limitwin \proxgame{X}
        \Rightarrow
      \pl D \limitwin \proxgame{H}
    $
  where $\limitwin$ is any of $\win$, $\ktactwin{k}$, or $\kmarkwin{k}$.
\end{thm}

\begin{proof}
  Let $\sigma\circ L$ witness $\pl D \limitwin \proxgame{X}$. We define
  $\tau\circ L$ for $\pl D$ in $\proxgame{H}$ as follows:
    \[
      \tau\circ L(p\rest n)
        =
      \sigma\circ L(p\rest n)
        \cap
      H^2
    \]

@@

\begin{thm}
  If $\pl D\limitwin \proxgame{X_i}$ for $i<\omega$, then
  $\pl D\limitwin \proxgame{\prod_{i<\omega}X_i}$, where $\limitwin$ is either
  $\win$ or $\kmarkwin{k}$.
\end{thm}

@@

  Let $\sigma_i\circ L$ witness $\pl D\limitwin \proxgame{X_i}$ for
  $i<\omega$, and assume without loss of generality that 
  $\sigma_i\circ L$ always yields $X_i^2$ before round $i$.

  Then we define the strategy $\tau\circ L$ for $\pl D$ in
  $\proxgame{\prod_{i<\omega}X_i}$ as follows:
    \[
      \tau\circ L(p\rest n)
        =
      \bigcap_{i\leq n} \pi_i^{-1}(\sigma_i\circ L(p_i\rest n))
    \]

@@

\begin{ex}
  $\pl D \markwin \proxgame{(\oneptcomp\kappa)^\omega}$
\end{ex}

\begin{proof}
  $\pl D \tactwin \proxgame{\oneptcomp\kappa}$ + previous result
\end{proof}

@@

\begin{lem}
  $\pl O\prewin\clusgame{X}{S}$ if and only if $\pl O\prewin\congame{X}{S}$.
\end{lem}

\begin{proof}
  Suppose that $\sigma$ is a predetermined winning strategy for 
  $\clusgame{X}{S}$. Let $p$ attack $\sigma$, and $q$ be a subsequence of $p$.
  It follows that $q$ also attacks $\sigma$, so $q$ clusters at $S$. Thus $p$
  conveges to $S$, and $\sigma$ is a predetermined winning strategy for 
  $\congame{X}{S}$.
\end{proof}

\begin{thm}
  For any predetermined absolutely proximal space $X$, 
  $\pl O\prewin \congame{X}{H}$ for all compact $H\subseteq X$.
\end{thm}

@@

  We now define the predetermined strategy $\tau$ for $\pl O$ in 
  $\clusgame{X}{H}$ such that:
  \[
    \tau(n) 
      = 
    \bigcup_{t\in\max(T(n))} 
      \bigcap_{m<2n+2}
        \frac{1}{4}\sigma(m)[h_{t\rest m+1}]
  \]
  noting that $\tau(n)=\bigcap_{m\leq n}\tau(m)$ by definition.

@@

  We have thus proven $\pl O\prewin\clusgame{X}{H}$, and thus
  $\pl O\prewin\congame{X}{H}$.
\end{proof}

@@

\begin{ex}
  Let $X=I\times 2$ be the Alexandrov double interval. Then 
  $\pl D \not\prewin \proxgame{X}$, but $\pl D \markwin \proxgame{X}$.
\end{ex}

@@

\begin{thm}
  For any uniformly locally compact space $X$,
      $\pl D\prewin \proxgame{X} \Leftrightarrow \pl D\prewin \aproxgame{X}$
\end{thm}

\begin{proof}
  Let $M$ be a uniformly locally compact entourage. 
  Let $\sigma$ witness $\pl D\prewin \proxgame{X}$ such that 
  $\sigma(n)\subseteq M$ always 
  (so $\cl{\sigma(a)[x]}\subseteq\cl{M[x]}$ is compact), 
  $\sigma(n+1)\subseteq\frac{1}{4}\sigma(n)$.

  Let $\tau(n)=\frac{1}{2}\sigma(n)$. If $p$ attacks $\tau$ in 
  $\aproxgame{X}$, then
    \[
      p(n+1)
        \in
      \tau(n)[p(n)]
        =
      \frac{1}{2}\sigma(n)[p(n)]
    \]

@@

\begin{prop}
If $\pl D \prewin \proxgame{X}$, then $X$ has a $G_\delta$ diagonal.
\end{prop}

\begin{proof}
  If $\pl D \prewin \proxgame{X}$ with strategy $\sigma$, then consider 
  $\<x,y\>\in \bigcap_{n<\omega} \sigma(n)$. It follows that 
  $\<x,y,x,y,\dots\>$ attacks $\sigma$, and 
    $
      \{x,y\}\subseteq \bigcap_{n<\omega} 
      \sigma(n)[x]\cap\bigcap_{n<\omega}\sigma(n)[y]
      \not=0
    $ 
  so it must converge, and $x=y$. Thus
  $\bigcap_{n<\omega}\sigma(n) = \Delta$ is $G_\delta$.
\end{proof}

>>>>

\begin{defn}
  For a uniform space $X$, the simplified proximal game $\bellConGame{X}$ can be defined as follows:

@@

\begin{thm}
  $\pl D$ has a winning perfect-information strategy in Bell's game if and only if $\pl D\win\bellConGame{X}$.
\end{thm}

@@

\begin{prop}
$\pl P$ has a winning perfect-information strategy in Bell's game if and only if $\pl P \win \bellConGame{X}$.
\end{prop}

@@

\begin{defn}
  A uniform space is \textbf{proximal} if $\pl D \win \bellConGame{X}$.
\end{defn}

\begin{defn}
  For a space $X$ and a point $x\in X$, the \textbf{$W$-convergence-game} $\gruConGame{X}{x}$ proceeds as follows.

@@

\begin{defn}
  A space is \textbf{$W$} if $\pl O \win \gruConGame{X}{x}$ for all $x\in X$.
\end{defn}

@@

\begin{thm}
For all $x\in X$:
  \begin{itemize}
    \item
      $\pl D\win \bellConGame{X} \Rightarrow \pl O \win \gruConGame{X}{x}$
    \item
      $\pl D\ktactwin{2k} \bellConGame{X} \Rightarrow \pl O \ktactwin{k} \gruConGame{X}{x}$
    \item
      $\pl D\kmarkwin{2k} \bellConGame{X} \Rightarrow \pl O \kmarkwin{k} \gruConGame{X}{x}$
  \end{itemize}
\end{thm}

\begin{proof}
Let $\sigma$ witness $\pl D \ktactwin{2k}\bellConGame{X}$ (resp. $\pl D \kmarkwin{2k}\bellConGame{X}$, $\pl D\win\bellConGame{X}$). We define the $k$-tactical (resp. $k$-Mark\"ov, perfect info) strategy $\tau$ such that
  \[
    \tau\circ L_k(p)
      =
    \sigma\circ L_{2k}(\<x,p(0),\dots,x,p(|p|-1)\>)[x]
      \cap
    \sigma\circ L_{2k}(\<x,p(0),\dots,x,p(|p|-1),x\>)[x]
  \]
where $L_{2k}$ is the $2k$-tactical fog-of-war (resp. $2k$-Mark\"ov fog-of-war, identity) and $L_{k}$ is the $k$-tactical fog-of-war (resp. $k$-Mark\"ov fog-of-war, identity).

@@

Certainly, $x\in E_{2n}[x]= E_{2n}[q(2n)]$ for any $n<\omega$. Note also for any $n<\omega$ that
    \[
      p(n) \in
      \bigcap_{m\leq n}\tau\circ L_k(p\rest n)
    \]
    \[
      =
      \bigcap_{m\leq n}\left(
        \sigma\circ L_{2k}(\<x,p(0),\dots,x,p(m-1)\>)[x]\cap
        \sigma\circ L_{2k}(\<x,p(0),\dots,x,p(m-1),x\>)[x]
      \right)
    \]
    \[
      =
      \bigcap_{m\leq n}\left(
        D_{2m}[x]\cap
        D_{2m+1}[x]
      \right) =
      \bigcap_{m\leq 2n+1} D_m[x]=E_{2n+1}[x]
    \]
so by the symmetry of $E_{2n+1}$, $x\in E_{2n+1}[p(n)]= E_{2n+1}[q(2n+1)]$. Thus $x\in \bigcap_{n<\omega} E_n[q(n)]\not=\emptyset$, and since $\sigma$ is a winning strategy, the attack $q$ converges. Since $q(2n)=x$, $q$ must converge to $x$. Thus its subsequence $p$ converges to $x$, and $\tau$ is a winning strategy in $\gruConGame{X}{x}$.
\end{proof}

\begin{cor}
For all $x\in X$:
  \begin{itemize}
    \item
      $\pl D\ktactwin{k} \bellConGame{X} \Rightarrow \pl O \ktactwin{k} \gruConGame{X}{x}$
    \item
      $\pl D\kmarkwin{k} \bellConGame{X} \Rightarrow \pl O \kmarkwin{k} \gruConGame{X}{x}$
  \end{itemize}
\end{cor}

@@

\begin{thm}
  Let $X\cup\{\infty\}$ be a uniformizable space such that $X$ is discrete. Then
  \begin{itemize}
    \item
      $\pl O\win \gruConGame{X\cup\{\infty\}}{\infty} \Rightarrow \pl D \win \bellConGame{X\cup\{\infty\}}$
    \item
      $\pl O\ktactwin{k} \gruConGame{X\cup\{\infty\}}{\infty} \Rightarrow \pl D \ktactwin{k} \bellConGame{X\cup\{\infty\}}$
    \item
      $\pl O\kmarkwin{k} \gruConGame{X\cup\{\infty\}}{\infty} \Rightarrow \pl D \kmarkwin{k} \bellConGame{X\cup\{\infty\}}$
  \end{itemize}
\end{thm}

@@

  Let $\sigma$ witness $\pl D \ktactwin{k}\gruConGame{X\cap\{\infty\}}{\infty}$ (resp. $\pl D \kmarkwin{k}\gruConGame{X\cap\{\infty\}}{\infty}$, $\pl D\win\gruConGame{X\cap\{\infty\}}{\infty}$). We define the $k$-tactical (resp. $k$-Mark\"ov, perfect info) strategy $\tau$ such that
    \[
      \tau\circ L(p)
        =
      D(\sigma\circ L(p))
    \]
  where $L$ is the $k$-tactical fog-of-war (resp. $k$-Mark\"ov fog-of-war, identity).

@@

\begin{cor}
  Let $X\cup\{\infty\}$ be a uniformizable space such that $X$ is discrete. Then
  \begin{itemize}
    \item
      $\pl O\win \gruConGame{X\cup\{\infty\}}{\infty} \Leftrightarrow \pl D \win \bellConGame{X\cup\{\infty\}}$
    \item
      $\pl O\ktactwin{k} \gruConGame{X\cup\{\infty\}}{\infty} \Leftrightarrow \pl D \ktactwin{k} \bellConGame{X\cup\{\infty\}}$
    \item
      $\pl O\kmarkwin{k} \gruConGame{X\cup\{\infty\}}{\infty} \Leftrightarrow \pl D \kmarkwin{k} \bellConGame{X\cup\{\infty\}}$
  \end{itemize}
\end{cor}

\begin{prop} For any $x\in X$ and $k\geq 1$,
  \begin{itemize}
    \item
      $\pl O\ktactwin{k}\gruConGame{X}{x} \Leftrightarrow \pl O\tactwin\gruConGame{X}{x}$
    \item
      $\pl O\kmarkwin{k}\gruConGame{X}{x} \Leftrightarrow \pl O\markwin\gruConGame{X}{x}$
  \end{itemize}
\end{prop}

\begin{proof}
  If $\sigma$ witnesses $\pl O\ktactwin{k}\gruConGame{X}{x}$, let $\tau(\emptyset)=\sigma(\emptyset)$ and
    \[
      \tau(\<q\>)
        =
      \bigcap_{i< k}
      \sigma(\<\underbrace{x,\dots,x}_{k-i-1},q,\underbrace{x,\dots,x}_{i}\>)
    \]

  This is easily verified to be a winning strategy. The proof for $\pl O\kmarkwin{k}\gruConGame{X}{x}$ is analogous.
\end{proof}

\begin{cor}
  Let $X\cup\{\infty\}$ be a uniformizable space such that $X$ is discrete, and $k\geq 1$. Then
  \begin{itemize}
    \item
      $\pl D\ktactwin{k}\bellConGame{X\cup\{\infty\}} \Leftrightarrow O\tactwin\bellConGame{X\cup\{\infty\}}$
    \item
      $\pl D\kmarkwin{k}\bellConGame{X\cup\{\infty\}} \Leftrightarrow O\markwin\bellConGame{X\cup\{\infty\}}$
  \end{itemize}
\end{cor}

\begin{prop} For any uniform space $X$,
  \begin{itemize}
    \item
      $\pl O\ktactwin{k}\bellConGame{X} \Leftrightarrow \pl O\ktactwin{2}\bellConGame{X}$
    \item
      $\pl O\kmarkwin{k}\bellConGame{X} \Leftrightarrow \pl O\kmarkwin{2}\bellConGame{X}$
  \end{itemize}
\end{prop}

\begin{proof}
  If $\sigma$ witnesses $\pl O\ktactwin{k}\bellConGame{X}{x}$, let $\tau(\emptyset)=\sigma(\emptyset)$ and
    \[
      \tau(\<q\>)
        =
      \bigcap_{i<k}
      \sigma(\<\underbrace{q,\dots,q}_{i}\>)
    \]
    \[
      \tau(\<q,q'\>)
        =
      \bigcap_{i< k}
      \sigma(\<\underbrace{q,\dots,q}_{k-i},\underbrace{q',\dots,q'}_{i}\>)
    \]

  This is easily verified to be a winning strategy. The proof for $\pl O\kmarkwin{k}\bellConGame{X}{x}$ is analogous.
\end{proof}

@@

\begin{defn}
  The absolute proximal game $\bellClusGame{X}$ is analogous to $\bellConGame{X}$, except $\pl D$ may only win if $p$ converges.
\end{defn}

@@

\begin{thm}
  For any uniformly locally compact space $X$,
      $\pl D\win \bellConGame{X} \Leftrightarrow \pl D\win \bellClusGame{X}$
\end{thm}

\begin{proof}
  Let $M$ be a uniformly locally compact entourage. Let $\sigma$ witness $\pl D\win \bellConGame{X}$ such that $\sigma(a)\subseteq M$ always (so $\cl{\sigma(a)[x]}\subseteq\cl{M[x]}$ is compact), and $a\supseteq b$  implies $\sigma(a)\subseteq\frac{1}{4}\sigma(b)$.

  Let $\tau(p\rest n)=\frac{1}{2}\sigma(p\rest n)$. If $p$ attacks $\tau$ in $\bellClusGame{X}$, then
    \[
      p(n+1)
        \in
      \tau(p\rest n)[p(n)]
        =
      \frac{1}{2}\sigma(p\rest n)[p(n)]
    \]

@@

  Finally, note that $p$ attacks the winning strategy $\sigma$ in $\bellConGame{X}$, but since the intersection of a chain of nonempty compact sets is nonempty:

@@

\begin{cor}
  A uniformaly locally compact space $X$ is proximal if and only if $\pl D \win \bellClusGame{X}$.
\end{cor}

\begin{thm}
  For any uniformly locally compact proximal space $X$, $\pl O\win \gruClusGame{X}{H}$ for all compact $H\subseteq X$.
\end{thm}

\begin{proof}
  Let $\sigma$ witness $\pl D \win \bellClusGame{X}$ such that $p\supseteq q$ implies $\sigma(p)\subseteq \frac{1}{4}\sigma(q)$.

@@

  With this we may define the perfect information strategy $\tau$ for $\pl O$ in $\gruConGame{X}{H}$ such that:
  \[
    \tau(p\rest n) = \bigcup_{s\concat\<i,h_{s,i},j\>\in\max(T(p\rest n))} \frac{1}{4}\sigma(o(s)\concat\<h_{s,i}\>)[h_{s,i,j}]
  \]

@@

  Let $q'=\<i_0,h_0,j_0,x_0,i_1,h_1,j_1,x_1,\dots\>$ correspond to this infinite branch in $T(p)$, and let $q=o(q')=\<h_0,x_0,h_1,x_1,\dots\>$. Note that by the construction of $T(p)$, $q$ is an attack on the winning strategy $\sigma$ in $\bellClusGame{X}$, so it must converge. Since every other term of $q$ is in $H$, it must converge to $H$. Then since $q$ is a subsequence of $p$, $p$ must cluster at $H$.
\end{proof}

\begin{cor}
  For any uniformly locally compact proximal space, $\pl O\win \gruConGame{X}{H}$ for all compact $H\subseteq X$.
\end{cor}

\begin{proof}
  $\pl O \win \gruConGame{X}{H}$ if and only if $\pl O \win \gruClusGame{X}{H}$.
\end{proof}

@@

\begin{thm}
  $\pl O \prewin \gruConGame{X}{H}$ if and only if there exists a countable base
  around $H$.
\end{thm}

@@

\begin{cor}
  $X$ is first countable if and only if $\pl O \prewin \gruConGame{X}{x}$ for
  all $x\in X$
\end{cor}

\begin{cor}
  $\pl D \prewin \bellConGame{X}$ implies $X$ is first countable.
\end{cor}

@@

\begin{cor}
  If $X$ is scattered compact and $\pl O \prewin\gruConGame{X}{x}$ for all
  $x\in X$ (or $\pl D \prewin\bellConGame{X}$), then $X$ is metrizable.
\end{cor}

\begin{ex}
  $\pl D \not\prewin \bellConGame{\oneptcomp\omega_1}$
\end{ex}

\begin{proof}
  There does not exist a countable base around $\infty$, so
    $\pl O \not\prewin \gruConGame{X}{\omega_1}$.
\end{proof}

\begin{ex}
  $\pl O \tactwin \gruConGame{\oneptcomp\kappa}{\infty}$ and
  $\pl D \tactwin \bellConGame{\oneptcomp\kappa}$ for all cardinals $\kappa$
\end{ex}

\begin{proof}
  For $\gruConGame{\oneptcomp\kappa}{\infty}$, let
    $\sigma()=\sigma(\infty)=\oneptcomp\kappa$
  and
    $\sigma(x)=\oneptcomp\kappa\setminus\{x\}$
  otherwise.
\end{proof}

@@

\begin{thm}
  If $H$ is a closed subset of $X$, then
    $
      \pl D \limitwin \bellConGame{X}
        \Rightarrow
      \pl D \limitwin \bellConGame{H}
    $
  where $\limitwin$ is any of $\win$, $\ktactwin{k}$, or $\kmarkwin{k}$.
\end{thm}

\begin{proof}
  Let $\sigma\circ L$ witness $\pl D \limitwin \bellConGame{X}$. We define
  $\tau\circ L$ for $\pl D$ in $\bellConGame{H}$ as follows:
    \[
      \tau\circ L(p\rest n)
        =
      \sigma\circ L(p\rest n)
        \cap
      H^2
    \]

@@

\begin{thm}
  If $\pl D\limitwin \bellConGame{X_i}$ for $i<\omega$, then
  $\pl D\limitwin \bellConGame{\prod_{i<\omega}X_i}$, where $\limitwin$ is either
  $\win$ or $\kmarkwin{k}$.
\end{thm}

@@

  Let $\sigma_i\circ L$ witness $\pl D\limitwin \bellConGame{X_i}$ for
  $i<\omega$, and assume without loss of generality that
  $\sigma_i\circ L$ always yields $X_i^2$ before round $i$.

  Then we define the strategy $\tau\circ L$ for $\pl D$ in
  $\bellConGame{\prod_{i<\omega}X_i}$ as follows:
    \[
      \tau\circ L(p\rest n)
        =
      \bigcap_{i\leq n} \pi_i^{-1}(\sigma_i\circ L(p_i\rest n))
    \]

@@

\begin{ex}
  $\pl D \markwin \bellConGame{(\oneptcomp\kappa)^\omega}$
\end{ex}

\begin{proof}
  $\pl D \tactwin \bellConGame{\oneptcomp\kappa}$ + previous result
\end{proof}

@@

\begin{lem}
  $\pl O\prewin\gruClusGame{X}{S}$ if and only if $\pl O\prewin\gruConGame{X}{S}$.
\end{lem}

\begin{proof}
  Suppose that $\sigma$ is a predetermined winning strategy for
  $\gruClusGame{X}{S}$. Let $p$ attack $\sigma$, and $q$ be a subsequence of $p$.
  It follows that $q$ also attacks $\sigma$, so $q$ clusters at $S$. Thus $p$
  conveges to $S$, and $\sigma$ is a predetermined winning strategy for
  $\gruConGame{X}{S}$.
\end{proof}

\begin{thm}
  For any predetermined absolutely proximal space $X$,
  $\pl O\prewin \gruConGame{X}{H}$ for all compact $H\subseteq X$.
\end{thm}

@@

  We now define the predetermined strategy $\tau$ for $\pl O$ in
  $\gruClusGame{X}{H}$ such that:
  \[
    \tau(n)
      =
    \bigcup_{t\in\max(T(n))}
      \bigcap_{m<2n+2}
        \frac{1}{4}\sigma(m)[h_{t\rest m+1}]
  \]
  noting that $\tau(n)=\bigcap_{m\leq n}\tau(m)$ by definition.

@@

  We have thus proven $\pl O\prewin\gruClusGame{X}{H}$, and thus
  $\pl O\prewin\gruConGame{X}{H}$.
\end{proof}

@@

\begin{ex}
  Let $X=I\times 2$ be the Alexandrov double interval. Then
  $\pl D \not\prewin \bellConGame{X}$, but $\pl D \markwin \bellConGame{X}$.
\end{ex}

@@

\begin{thm}
  For any uniformly locally compact space $X$,
      $\pl D\prewin \bellConGame{X} \Leftrightarrow \pl D\prewin \bellClusGame{X}$
\end{thm}

\begin{proof}
  Let $M$ be a uniformly locally compact entourage.
  Let $\sigma$ witness $\pl D\prewin \bellConGame{X}$ such that
  $\sigma(n)\subseteq M$ always
  (so $\cl{\sigma(a)[x]}\subseteq\cl{M[x]}$ is compact),
  $\sigma(n+1)\subseteq\frac{1}{4}\sigma(n)$.

  Let $\tau(n)=\frac{1}{2}\sigma(n)$. If $p$ attacks $\tau$ in
  $\bellClusGame{X}$, then
    \[
      p(n+1)
        \in
      \tau(n)[p(n)]
        =
      \frac{1}{2}\sigma(n)[p(n)]
    \]

@@

\begin{prop}
If $\pl D \prewin \bellConGame{X}$, then $X$ has a $G_\delta$ diagonal.
\end{prop}

\begin{proof}
  If $\pl D \prewin \bellConGame{X}$ with strategy $\sigma$, then consider
  $\<x,y\>\in \bigcap_{n<\omega} \sigma(n)$. It follows that
  $\<x,y,x,y,\dots\>$ attacks $\sigma$, and
    $
      \{x,y\}\subseteq \bigcap_{n<\omega}
      \sigma(n)[x]\cap\bigcap_{n<\omega}\sigma(n)[y]
      \not=0
    $
  so it must converge, and $x=y$. Thus
  $\bigcap_{n<\omega}\sigma(n) = \Delta$ is $G_\delta$.
\end{proof}
